Equity conceptualizations and standards within transportation literature: a scoping review

### 2023-10-24 Manuscript/Manuscript.qmd
With the template "executive summary", "reading guide" and "glossary" sections.

```{r echo=FALSE}
#function for creating comments
word_comment <- function(comment, highlight = "") {
  if (isTRUE(knitr:::pandoc_to() == "docx")) {
    paste0('[', comment, ']{.comment-start id="0" author="Anastasia"',
           'date="2023-08-12T15:00:00Z"}', highlight, '[]{.comment-end id="0"}')
  }
}
```

>>>>

```{r echo=FALSE}
#function for creating comments
word_comment <- function(comment, highlight = "") {
  if (isTRUE(knitr:::pandoc_to() == "docx")) {
    paste0('[', comment, ']{.comment-start id="0" author="Anastasia"',
           'date="2023-08-12T15:00:00Z"}', highlight, '[]{.comment-end id="0"}')
  }
}
```
# Executive Summary

_If we plan to write an executive summary, it should ease readers into the report. The full report is long so this may be a useful 2-3 page summary addition._

# Reading guide

_This portion may be helpful to guide readers to desired sections, if they are not interested in reading the full report. For instance:_

_- If you're interested in why we wrote this report read the "Introduction."_
_- Curious about the conceptual framework for transport justice? Read the framework in "A framework to analyze questions of justice"_
_- Want to know about our calls for action to move transport equity analysis and standard-setting substantively towards questions of transport justice? Read the "Moving forward: concluding remarks and calls for action". This section is geared to both researchers and decision-makers._

# Glossary
_This section may be helpful for readers to clarify our definitions of these terms so they can more easily follow the text and as a quick reference:_

- Fair: 
- Justice: 
- Equity: 
- Equality:
- Dimensions:
- Conceptualizations:

Etc.,
